XX

### 2019-05-26 paper/manuscript.Rmd
Add worldmap of study sites

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)

@@

all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
  glue::glue_collapse(sep = "; ") %>%
  paste0("[", ., "]")
```

@@

Studies are `r all_int_cites`

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300, 
                      eval.after = "fig.cap")

@@

```

@@

```{r, fig.cap=paste("Graph of", all_int_cites, "data points")}
loadd(fig_worldmap)

all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
  glue::glue_collapse(sep = "; ") %>%
  paste0("[", ., "]")

fig_worldmap
```

Studies are
